How economic, health and social factors affect life expectancy in developing countries?

### 2025-04-10 paper.Rmd
fixed formatting

$$
\begin{aligned}
\hat{\text{LifeExpectancy}} =\ & 57.86 \\
& - 0.374 \times \text{InfantDeaths\_lg1p} \\
& - 6.228 \times \text{HIV\_AIDS\_lg1p} \\
& + 1.067 \times \text{Schooling} \\
& + 0.541 \times \text{PercentageExpenditure\_lg1p} \\
& - 1.511 \times \text{AlcoholNegligible}
\end{aligned}
$$

@@

kable(results, col.names = c("Term", "Estimate", "Std. Error", "t value", "Pr(>|t|)", 
                            "95% CI Lower", "95% CI Upper"), 
      caption = "Final Regression Results")

@@

```{r}
#| label: fig-stepwiseplots
#| layout-ncol: 2
#| fig-align: "center"
#| warning: false
#| message: false
#| echo: false

>>>>

$$
\begin{aligned}
\hat{\text{LifeExpectancy}} =\ & 57.86 \\
& - 0.374 \times \log(1 + \text{Infant Deaths}) \\
& - 6.228 \times \log(1 + \text{HIV/AIDS Deaths}) \\
& + 1.067 \times \text{Schooling} \\
& + 0.541 \times \log(1 + \text{Health Expenditure (as percentage of GDP per capita)}) \\
& - 1.511 \times \text{AlcoholNegligible}
\end{aligned}
$$

@@

# rounding to 3 decimal places
results$Estimate     <- round(results$Estimate, 3)
results$Std_Error    <- round(results$Std_Error, 3)
results$t_value      <- round(results$t_value, 3)
results$LowerBound95 <- round(results$LowerBound95, 3)
results$UpperBound95 <- round(results$UpperBound95, 3)

kable(results, col.names = c("Term", "Coefficent Estimates", "Std. Error", "t value", "Pr(>|t|)", 
                            "95% CI Lower", "95% CI Upper"), 
      caption = "Final Regression Results")

@@

```{r}
#| label: fig-stepwiseplots
#| fig-align: "center"
#| warning: false
#| message: false
#| echo: false
